\section{Conclusion}
\subsection{Limitations}
The proposed framework is subject to several physical, technical, and technological limitations. A key concern is measurement accuracy: high-precision, standardized instruments would be required at each node to ensure fairness across the system.\\
The stability of the grid has not been analyzed in this work and should be investigated through simulations to better understand the resulting economic dynamics. In addition, nodes would need sufficient energy storage capacity to avoid persistent push-only behavior, and decentralized elections should remain independent of large transfer hubs.\\
Finally, the server and its surrounding ecosystem must demonstrate adequate resilience to cyber threats, as well as sufficient computational capacity to execute smart contracts and calculate grid-level properties.
\subsection{Emergent network behavior}
Two types of behavior arise in the grid due to the nature of the framework:\begin{itemize}
    \item Taxation: taxation appears in cross-transactions as intermediaries deliver efficiency close to that expected whilst physical efficiency is higher, thus keeping the difference to themselves. The model rewards higher grid efficiency than expected, and thus incentivize nodes to be energetically sustainable.\\
    Intermediaries act as lenders of infrastructure and receive in exchange the efficiency difference, mimicking fee-like payments.
    \item Strong linking: nodes which actively exchange energy naturally increase their $Y$ matrix exergy and thus their voting power. In order to increase a node's power and influence on the grid, then, actively participating on the economy is key since it increases the node's entries on the $Y$ matrix.
\end{itemize}
Simulations are required to further understand the scope of these and other tendencies.
\subsection{Directions for future research}
Future research may explore and expand the framework in several directions:\begin{itemize}
    \item Incorporating simulations to study system behavior
    \item Allowing for directed connections between nodes
    \item Modeling real energy exchange and transaction log blockchain fields
\end{itemize}
\bibliographystyle{plain}
\bibliography{references}